On hyperparameter tuning through Lipschitz global optimization

### 2024-03-18 2024/ITMO paper/sn-article.tex
Declarations ans Statements, References

%%\documentclass[sn-nature]{sn-jnl}% Style for submissions to Nature Portfolio journals
%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
%\documentclass[sn-mathphys-num]{sn-jnl}% Math and Physical Sciences Numbered Reference Style 
\documentclass[iicol]{sn-jnl}
%%\documentclass[sn-mathphys-ay]{sn-jnl}% Math and Physical Sciences Author Year Reference Style
%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[sn-vancouver,Numbered]{sn-jnl}% Vancouver Reference Style
%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style 
%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style

@@

\usepackage[round]{natbib}
\bibliographystyle{abbrvnat}
%\setcitestyle{authoryear,open={(},close={)}} %Citation-related commands

@@

%\backmatter
\bmhead{Supplementary information}

The software that implements all of the described methods is available in the open repository \url{https://github.com/aimclub/iOpt/}.
Python scripts that reproduce the results of the experiments described in this paper are available in the benchmarks folder.

\bmhead{Acknowledgements}

The research was carried out within the state assignment of Ministry of Science and Higher Education of the Russian Federation (project No FSER-2024-0004).

@@

\section*{Declarations}

The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

@@

%\bibliographystyle{abbrvnat}
\bibliography{sn-bibliography}
% common bib file
%% if required, the content of .bbl file can be included here once bbl is generated
%%\input sn-article.bbl

>>>>

%%\documentclass[sn-nature]{sn-jnl}% Style for submissions to Nature Portfolio journals
%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
%\documentclass[sn-mathphys-num]{sn-jnl}% Math and Physical Sciences Numbered Reference Style 
\documentclass[lineno,iicol]{sn-jnl}
%%\documentclass[sn-mathphys-ay]{sn-jnl}% Math and Physical Sciences Author Year Reference Style
%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[sn-vancouver,Numbered]{sn-jnl}% Vancouver Reference Style
%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style 
%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style

@@

%\usepackage[pagewise]{lineno}

\usepackage[round]{natbib}
%\setcitestyle{authoryear,open={(},close={)}} %Citation-related commands

@@

%\backmatter
%\bmhead{Supplementary information}

%The software that implements all of the described methods is available in the open repository \url{https://github.com/aimclub/iOpt/}.
%Python scripts that reproduce the results of the experiments described in this paper are available in the benchmarks folder.

%\bmhead{Acknowledgements}

%The research was carried out within the state assignment of Ministry of Science and Higher Education of the Russian Federation (project No FSER-2024-0004).

@@

\section*{Statements and Declarations}

\textbf{Funding} The research was carried out within the state assignment of Ministry of Science and Higher Education of the Russian Federation (project No FSER-2024-0004).

\noindent
\textbf{Competing Interests} The authors have no relevant financial or non-financial interests to disclose.

\noindent
\textbf{Data Availability} 
The datasets analyzed during the current study are available in the UCI Machine Learning Repository, \url{https://archive.ics.uci.edu/}. 
The software that implements all of the described methods is available in the open repository \url{https://github.com/aimclub/iOpt/}.
Python scripts that reproduce the results of the experiments described in this paper are available in the benchmarks folder.

%The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\section*{Compliance with Ethical Standards}

\textbf{Conflict of interest} The authors declare that they have no conflict of interest.

\noindent
\textbf{Ethical approval} This article does not contain any studies with human participants or animals performed by any of the authors.

@@

\bibliographystyle{sn-basic}
\bibliography{sn-bibliography}
% common bib file
%% if required, the content of .bbl file can be included here once bbl is generated
%%\input sn-article.bbl
